---
title: "Homework_4"
author: "Alphonso Saiewane, Emmenta Janneh, Miles Matthews"
date: "2024-02-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
data("iris")
```

# Question 1a

```{r}
nrow(iris)

iris %>% 
  pmap_dbl(~., nrow) %>% length()
```

## Question 1b
```{r}
#map(iris, unique)

iris %>% 
  unique() |> 
  map(~., nrow)
```

# Question 2
```{r}
sub_mat <- matrix(nrow = 3, ncol = 5)
for(i in 1:3){
  for(j in 1:5){
    sub_mat[i,j] = j - i
  }
}
sub_mat
```


# Question 3

First tibble:

```{r}
rnorms_list <- list(negative_10 = c(rnorm(n = 10, mean = -10)),
                  zero = c(rnorm(n = 10, mean = 0)),
                  ten = c(rnorm(n = 10, mean = 10)),
                  hundred = c(rnorm(n = 10, mean = 100))
)


rnorms_tibble <- as_tibble(rnorms_list)
View(rnorms_tibble)
```

Second tibble:

```{r}
rnorms_list <- list(negative_10 = c(rnorm(n = 10, mean = -10)),
                  zero = c(rnorm(n = 10, mean = 0)),
                  ten = c(rnorm(n = 10, mean = 10)),
                  hundred = c(rnorm(n = 10, mean = 100))
)


rnorms_tibble <- as_tibble(rnorms_list)
View(rnorms_tibble)
```

# Question 4a
```{r}
X <- list(12, 14, 15, 18, 19, 22,10,18,18)
Mean <- list(16, 16, 16, 16, 16,16,16,16,16)
sd <- list(2, 2, 2, 2, 2,2,2,2,2)

pmap_dbl(list(X,Mean,sd), function(x,y,z)((x - y) / z))
```

# Question 4b
```{r}
pmap_dbl(list(X, Mean, sd), function(x,y,z)(((x-y)/z)/sqrt(length(X))))
```

# Question 5a
```{r}
V = c(10,15,17,22,32,38,42)
keep(V, function(x) x < 20)
```

# Question 5b
```{r}
discard(V, function(a) a < 20)
```

# Question 6
```{r}
U = list(10,15,"mary",22,32,"james",42)
map(U, safely(~ .x + 15))
```

The function `safely()` is used to test the execution of an operation on an object. It returns 
two output for every execution - Result and Error. If an operational execution will be successful,
it returns the success value in Result and NULL in Error. If the execution will be unsuccessful,
it returns NULL in Result and the error message in Error. In our execution, the test the addidion 
of 15 to each element in our list V. From the safely() output, we see that all V elements that are
numeric has the + 15 value as Result and Error NULL. This shows that for those elements, the 
execution is successful. However, for the character elements in V, we have an output of Result Null 
and Error <simpleError in .x + 15: non-numeric argument to binary operator>, indicating an 
unsuccessful execution.



Credit to https://www.geeksforgeeks.org/how-to-convert-a-list-to-a-dataframe-in-r/ for reference. 


