---
title: "Homework3_Week3"
author: "Group I (Alphonso Saiewane, Miles Matthews, and Emmenta Janneh)"
date: "2024-02-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

###Creating Vector1
```{r}
Vector1 <- (c( 10, 19, 121, 83, 63, 7, 77, 61, 51, 97, 123, 41))
```


###Question 1

#### Method 1:
```{r}
Vector1[c(1,12)]
```

#### Method 2:
```{r}
str(Vector1[c(1,12)])
```


### Question 2

#### Method 1
```{r}
Vector1[Vector1 < 60]
```


#### Method 2
```{r}
Vector1[Vector1 %% 60 == Vector1]
```

### Question 3

#### Method 1
```{r}
Vector1[Vector1 %% 2 != 0 & Vector1 %% 3 != 0]
```

#### Method 2
```{r}
Vector1[Vector1 %% 2 > 0 & Vector1 %% 3 > 0]
```



4)  Use and show two R coding methods to confirm that Vector1 does not have missing values


```{r}
# Define the list
myList <- list(TRUE, 12.35, "pear", 48, c = 3:8, list(23, "team"))

# Extract Vector1 from the list
Vector1 <- unlist(myList)

# Check for missing values in Vector1 using anyNA()
missing_values <- anyNA(Vector1)
print(!missing_values)
```


```{r}
# Define the list
myList <- list(TRUE, 12.35, "pear", 48, c = 3:8, list(23, "team"))

# Extract Vector1 from the list
Vector1 <- unlist(myList)

# Check if Vector1 has any missing values
no_missing_values <- all(!is.na(Vector1))
print(no_missing_values)
```

5) For the list given above, use and show R coding to confirm that “pear” is a character element.

```{r}
# Define the list
myList <- list(TRUE, 12.35, "pear", 48, c = 3:8, list(23, "team"))

# Check if "pear" is a character element
is_character <- typeof(myList[[3]]) == "character"
print(is_character)
```

6) For the list given above, use and show R coding to extract the first three elements of the list.


```{r}
# Define the list
myList <- list(TRUE, 12.35, "pear", 48, c(3:8), list(23, "team"))

# Extract the first three elements
first_three <- myList[1:3]
print(first_three)
```



### Question 7
Use the $ operator to extract the element “pear” from your list. Be sure to use and show
required R code to produce the requested output.
```{r}
myList1 <- list(TRUE, 12.35, p = "pear", 48, c = 3:8, list(23, "team"))
myList1$p
```

### Question 8
```{r}
qsolve <- function(a, b, c){
  discriminant <- b^2 - 4*a*c
  
  if(discriminant < 0){
    return("No real values")
  }
  else{
    value1 <- (-b + sqrt(discriminant)) / (2*a)
    value2 <- (-b - sqrt(discriminant)) / (2*a)
    
    return(c(value1, value2))
  }
}
```
#### 8a
```{r}
qsolve(1, -3, -28)
```

#### 8b
```{r}
qsolve(1, 1, -30)
```

#### 8c
```{r}
qsolve(3, 14, 8)
```

#### 8d
```{r}
qsolve(2, 11, -6)
```

### Question 9
```{r}
Tibble_call <- tibble(x = seq(1,10),
                      y = seq(10,1),
                      z = seq(5,.5, -0.5)
                    )
Tibble_call
```

### Question 10
```{r}
Tibble_call %>% 
  map_dbl(
    ~{
      q1 <- quantile(., 0.25)
      q3 <- quantile(., 0.75)
      iqr <- q3 - q1
      return(iqr)
    }
  )
```
