---
title: "data.table_classLab"
author: "Emmenta Janneh"
date: "2024-03-18"
output: html_document
---

```{r}
library(tidyverse)
library(dplyr)
library(data.table)
flights <- fread("nycdata.csv")
tlights <- read_csv("nycdata.csv")
```

1) Use and show data.table code to select the variables year, month, day, and hour from the
imported flights data
```{r}
flights[,.(year, month, day, hour)]
```

2) Use and show data. table code to produce a table that shows a carrier of DL, an origin of JFK
and a destination of SEA
```{r}
flights[carrier == "DL" & origin == "JFK" & dest == "SEA"]
```

3) Use and show data.table code to produce a table that shows a carrier of UA, a month of
March, and an airtime that is below 330.
```{r}
flights[carrier == "UA" & month == 3 & air_time < 330]
```

4) Use and show tidyverse code to produce a table that shows a carrier of UA, a month of
March, and an airtime that is below 330.
```{r}
tlights |>
  select(carrier, month, air_time) |>
  filter(carrier == "UA", month == 3, air_time < 330)
```

5) Use the data.table method to add a variable called speed that is the average air speed of
the plane in miles per hour.
```{r}
flights[, c("speed") := .(distance / (air_time/60))]
flights
```

6) Use the tidyverse method to add a variable called speed that is the average air speed of the
plane in miles per hour.
```{r}
tlights |>
  mutate(speed = distance / (air_time/60)) -> tlights
tlights
```

7)
Show and use coding to change the carrier abbreviation of UA to UniitedAir,
7a) data.table method
```{r}
flights[carrier == "UA", carrier := "UniitedAir"]
flights
```

7b tidyverse method (Use a sequence of dplyr commands so that you can see the change in
your table)
```{r}
tlights |> 
  mutate(carrier = recode(carrier, "UA" = "UniitedAir")) -> tlights
tlights |>
  filter(carrier == "UniitedAir")
```



