---
title: "Midterms"
author: "Emmenta Janneh"
date: "2024-03-09"
output: html_document
---

```{r}
library(tidyverse)
```

### 1

```{r}
Three_and_Four <- function(x){
  if(x %% 3 == 0 && x %% 4 == 0){
    print("This number is divisible by both 3 and 4.")
  }
  else{
    print("This number is not divisible by both 3 and 4. ")
  }
}

Three_and_Four(744)

Three_and_Four(159)
```

### 2

```{r}
diffcube <- function(x){
  x^3 - x^2
}
diffcube(5:1)
```

### 3

```{r}
U <- c("Maine" , "Texas", "Delaware", "Oregon", "Utah", "Vermont", "Ohio")
```

#### a

The variable U is an example of an atomic vector. An atomic vector is a basic data structure that can hold elements of the same data type.

#### b

```{r}
U[5]
U[U == "Utah"]
```

#### c

```{r}
U[-7]
U[U != "Ohio"]
```

### 4

```{r}
V = list("Chicago", k = list( 2, 6, 18, 24, 36), FALSE, 13, 1.3, z = 1:20)
```

#### a

The variable V is an example of a List A list is a versatile data structure that can store heterogeneous elements, meaning it can contain objects of different data types. Unlike atomic vectors, lists can hold elements such as vectors, matrices, data frames, and even other lists. In the case of V, we see character, List, Logical, and Numbers.

#### b

```{r}
V[[2]]
```

#### c

```{r}
typeof(V[[3]])
```

### 5

```{r}
tribble( ~John, ~Raymond, ~Martha, ~Alice, ~Juan,
86, 77, 81, 88, 90,
79, 78, 85, 81, 78,
76, 75, 88, 94, 81,
84, 90, 71, 84, 89,
100, 80, 93, 85, 84,
90, 73, 70, 88, 93
) -> TestScores
TestScores
```

#### a

```{r}
map_dbl(TestScores, mean)
```

#### b

```{r}
as.data.frame(map(TestScores, function(x)(x^3)))
```

#### c

```{r}
as.data.frame(map(TestScores, function(x)(x - x + 100)))
```

### 6

```{r}
thematrix <- matrix(ncol = 4, nrow = 4)
for(i in 1:nrow(thematrix)){
  for(j in 1:ncol(thematrix)){
    thematrix[i, j] = (i * j)^2
  }
}
thematrix
```

### 7

- `git clone`: This command is used in Git, to create a copy of a repository. This command is particularly useful when you want to obtain a local copy of a remote Git repository.
- `git init`: This command is used in Git to initialize a new and empty Git repository in a directory. When you run `git init`, it sets up the necessary data structures and files that Git uses to manage version control for your project.
- `ls`: The `ls` command is a commonly used command in Unix-like operating system. It is used to list the files and directories in the current working directory.
- `git add`: This command is used to add changes in your working directory to the staging area. In Git, changes to files go through a two-step process before thay are committed.
- `touch`: This command is a command-line utility used in Unix-like operating systems to create an empty file or update the access and modification timestamos of an existing file.
- `git push -u`: This command is used in Git to push local changes to a remote repository, and the `-u` flag is used to set up tracking information between the local and remote branches.
- `git commit -m`: The git commit -m command is used in Git to create a new commit with a specified commit message. Commits in Git represent a snapshot of your project's state at a particular point in time. The -m flag allows you to include a short and descriptive message directly in the command line without opening a text editor, making it a quick way to document changes.
- `git branch`: The git branch command is used in Git to list, create, or delete branches within a Git repository. Branches in Git are essentially pointers to a specific commit, allowing you to work on different features or changes in isolation.
- `git merge`: This command is used to combine changes from different branches. Merging allows you to integrate the changes made in one branch into another, typically bringing the changes from a feature branch into the main branch.
